---
title: "Chickwts"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1.) Find the mean weight and the median weight of all of the chicks.

```{r}
data("chickwts")

mean_weight <- mean(chickwts$weight)
median_weight <- median(chickwts$weight)

data("chickwts")

mean_weight <- mean(chickwts$weight)
median_weight <- median(chickwts$weight)

print(paste("Mean weight of the chicks:", mean_weight))
print(paste("Median weight of the chicks:", median_weight))

```

# 2.) Which feed was the heaviest chick given?
```{r}
data(chickwts)

max_weight <- max(chickwts$weight)
heaviest_feed <- chickwts$feed[chickwts$weight == max_weight]

print(paste("Heaviest chick weight =", max_weight, "grams & was given", heaviest_feed, "feed."))
```


# 3.) Which feed was the lightest chick given?
```{r}
data(chickwts)

min_weight <- min(chickwts$weight)
lightest_feed <- chickwts$feed[chickwts$weight == min_weight]

print(paste("Lightest chick weight =", min_weight, "grams & was given", lightest_feed, "feed."))

```


# 4.) Create a diagram that shows box plots side-by-side to compare the chick weights by feed type.
```{r}
library(ggplot2)
data(chickwts)

ggplot(chickwts, aes(x = feed, y = weight, fill = feed)) +
  geom_boxplot() +
  labs(title = "Chick Weights by Feed Type", x = "Feed Type", y = "Weight in grams") +
  theme_minimal() +
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5))  

```

# 5.) According to these box plots, which two feed types resulted in the heaviest chicks.

```{r}
library(ggplot2)
data(chickwts)

ggplot(chickwts, aes(x = reorder(feed, -weight, median), y = weight, fill = feed)) +
  geom_boxplot() +
  labs(title = "Chick Weights by Feed Type", x = "Feed Type", y = "Weight in grams") +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(hjust = 0.5)
  )

```

**So the heaviest chicks were fed Casein (and the lightest horsebean).**

